%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Architect / Developer} % Job title
{Isladentro Website } % Organization
{Havana, Cuba.} % Location
{2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implement a website solution for the Isladentro team, to present the information of their business on internet. Using Joomla CMS and creating severals custom modules to present their information on the web}
\item {Joomla/ MySQL/ {PHP}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Architect / Developer} % Job title
{Random Data Generator for NoSQL Databases} % Organization
{University of Informatics Sciences, Havana, Cuba.} % Location
{2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Design and implement a desktop solution using Python and PyQT4 library to populate the NoSQL databases using a random data generation by specifying some restriction parameters in the application.}
\item {Python/ PyQT4/ MongoDB/ Cassandra/ Neo4j/ Redis}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Configuration Manager} % Job title
{Web servers configuration (Apache / Nginx)} % Organization
{University of Informatics Sciences, Havana, Cuba.} % Location
{2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Deployment and configure several applications in web servers like Apache and Nginx.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Management Statistics Information System (SIGE)} % Job title
{Center of Technologies and Data Management (University of Informatics Science)} % Organization
{La Havana, Cuba} % Location
{2013 - 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Design and implementation of statistical computer systems (SIGE) adaptable to different environment and/or business}
\item {FullStack Developer/ Project Manager/ Architect/ Team Leader}
\item {PHP/ ExtJs/ Javascript}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Developer} % Job title
{Accident Sketch (AS)} % Organization
{Dofleini Team, Havana, Cuba} % Location
{2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implement a solution using AngularJS and JHipster to draw sketches of accidents and execute little kinetics simulations.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Developer} % Job title
{Police Management System (PMS)} % Organization
{Dofleini Team, Havana, Cuba} % Location
{2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {It’s a custom development for police stations in Tarragona Spain. Specially design to cover the main needs of police daily}
\item {FullStack Developer}
\item {AngularJS/ Java Spring /JHipster}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Developer} % Job title
{Bloomingdales Prototype} % Organization
{BlueOcean Tech, Havana, Cuba} % Location
{2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Develop a web market prototype to show products and its details.}
\item {AngularJS/ ES6 /SASS}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Developer} % Job title
{LEAP App} % Organization
{BlueOcean Tech, Havana, Cuba} % Location
{2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {http://leapbrands-all.leapmediainvestments.com}
\item {LEAP show the result of a survey made in US about Brands and TV Programs.}
\item {FrontEnd Developer}
\item {AngularJS/ Google Charts/ jsPdf}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Developer} % Job title
{Gophr App} % Organization
{BlueOcean Tech, Havana, Cuba} % Location
{2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {http://www.gogophr.com}
\item {GoGophr is an innovative digital library which is built by searching across the web using major search engines and building your own portal with the best of content on the concerned subject matter.}
\item {FullStack Developer}
\item {Microservice Architecture/ AngularJS/ Java/ Scala/ NodeJS/ Reactive Programing}
\end{cvitems}
}

%------------------------------------------------
\end{cventries}

